\thetitle

### 2021-01-12 paper/paper.tex
results 1

\section{Preliminary Results}
\label{sec:Preliminary}

@@

@@

\begin{table}[t]
  \centering
        %         \def\arraystretch{1.2}          %  1 is the default, change whatever you need

  \begin{tabular}{|l||c|c|c|c|c|c|c|c|c|c|}
    \hline
    Parameter & $\alpha$ & $\beta$ & $\delta$ & $\gamma$ & $\epsilon$ & $p_{exp}$ & $\xi$ \\
    \hline
    Value & 0.5 & 0.15 & 0.15 & 0.15 & 0.5 & 1.0 & 0.15 \\
    \hline
  \end{tabular}

        %         \egroup

  \caption{\label{tbl:params}Parameter Setup.}
        %         \end{figure}
\end{table}

Table~\ref{tbl:res} shows the results, where we evaluate the average reward and discounted
reinforcement learning algorithm by providing either direct reward feedback, that is the reward
accumulated in the next period, without keeping track of any orders, as \(\ActShipped\) and
\(\ActShippedDQN\) respectively. Further both algorithms are evaluated with keeping track of the
order pool orders, such that each action is responsible for all orders in the order pool. These are
labelled \(\ActOrdPool\) and \(\ActOrdPoolDQN\). For comparisons reasons we provide
\(\BILOne-\BILSix\) and immediate release (interval release).

The results show that at the current time we are facing issues with scaling the algorithm to the
order release problem. Likely this is due to parameterisation issues, which we are investigating
currently. However, it can be seen that i) the technique of keeping track of the order pool orders
leads to better policies and ii) that despite the parameterisation issues average reward
reinforcement learning finds better solutions than its discounted counterpart. However, the least
costs are generated by \(\BILThree\), which shows that there is room for improvement for the
reinforcement learning policies.

Interesting is also to see, that all reinforcement learning variants are releasing rather late,
leading to low finished goods inventory costs (FGIC), but high backorder costs (BOC). Furthermore,
the agents based on the order-pool orders, namely \(\ActOrdPool\) and \(\ActOrdPoolDQN\), are able
achieve lower work-in-process costs (WIPC) and also lower tardiness, than the other the agents
rewarded directly on the shipped orders.

\begin{table}[t!]
  \centering
  \def\arraystretch{1.2}          %  1 is the default, change whatever you need
  \setlength\tabcolsep{4pt}
  \begin{tabular}{|l||c|c|c|c|c|c|c|c|c|}
    % BEGIN RECEIVE ORGTBL res2
    \hline
    Algorithm/KPI & SUM & BOC & FGIC & WIPC & % \%SL &
                                                       TARD & \(\sigma\)TARD & SFTT\\
    \hline
    % Evaluation 1 & \multicolumn{11}{c|}{} \\
    \ActShipped    & 1777.74 & 1322.04 & 94.49 & 361.20       & 2.24 & 1.52 & 3.44\\
    \ActOrdPool    & 1593.03 & 1318.65 &14.01 &260.36         & 2.11 & 1.42 & 2.68\\
    \ActShippedDQN & 1940.62 & 1570.40 &6.30 &363.92          & 2.35 & 1.59 & 3.95 \\
    \ActOrdPoolDQN & 1618.88 & 1306.20 & 40.68& 272.00        & 2.08 & 1.38 & 2.58\\
    \BILOne        & 1736.98 & 1510.42  &  0.00  & 226.56     & 2.04 & 1.26 & 2.16 \\
    \BILTwo        & 1081.79 & 769.86 & 86.89   & 225.03      & 1.87 & 1.18 & 2.15\\
    \BILThree      &  \textbf{922.36} & 362.59 &  334.47  & 225.30     & 1.74 & 1.07 & 2.15\\
    \BILFour       & 1062.68 & 155.72  & 681.03   & 225.93    & 1.63 & 0.99 & 2.15\\
    \BILFive       & 1380.04 & 65.45  & 1088.94    & 225.64   & 1.67 & 1.02 & 2.15\\
    \BILSix        & 1777.77 & 25.04 &  1529.77  & 222.96     & 1.61 & 0.85 & 2.13\\
    \imre          & 2209.97 & 12.08 &1974.72 & 223.16        & 1.58 & 0.63 & 2.14 \\
    \hline
    % END RECEIVE ORGTBL res2
  \end{tabular}
        %         \egroup

  \caption{\label{tbl:res}Evaluation results where the monetary units are in \(k\)-values.}

        %         \end{figure}
\end{table}

@@

This paper introduces deep theoretical insights in reinfocement learning and provides first evidence
that average reward reinfocement learning is better applicable to operations research problems than
the discounted framework.
        %         adds to the growing body of evidence that machine learning algorithms can contribute
        %         positively to a company's performance.
The paper describes an % successful
application of an order release model based on reinforcement learning. The performance is tested on
a multi-product, two-stage hypothetical flow shop and is measured by cost, delivery and lead time
related measures. We show that in the current version the machine learning approach is not able to
outperform all other tested order release
approaches. % By yielding lower \textit{UPDATE: total costs,
        %         less mean and standard deviation of tardiness and a shorter shop floor throughput time (SFTT)}.
        %         Despite the good performance of our proposed adaptive order release model based on \textit{UPDATE:
        %         reinforcement learning} we are aware of its limitations. Firstly, the results are limited to the
        %         simulated case and the validity of the results for other production systems must be assessed in
        %         future studies. Secondly, adding further experimental factors would be beneficial like including
        %         scenarios with machine failures and different scheduling rules. In conclusion we found that our
        %         proposed adaptive order release approach harbours enormous potential.
In the future we expect to be able to yield better results by investigating the parameterisation and
resolving current issues when scaling average reinforcement learning to complex scenarios.

@@

\vfill
\pagebreak
\appendix

\section{N-Discount-Optimality}
\label{sec:methods}

This part proves (or rather ought to prove, as this is only the first version of such a proof)
Blackwell-optimality of the average reward adjusted reinforcement learning algorithm shown in
Algorithm~\ref{alg:near}. The idea is to prove \(n\)-discount optimality for \(n=-1\), \(n=0\), and
finally for \(n \geqslant 1\). But first recall the definition of \(n\)-discount-optimality.

\begin{definition*}
  Due to \cite{Veinott69} for MDPs a policy \(\polopt\) is \emph{\(n\)-discount-optimal} for
  \(n=-1,0,1,\ldots\) for all states \(s \in \States\) with discount factor
  \(\gamma\) % and \(V_{\gamma}^{\pol}(s)\) being the value function as defined above
        %
  if and only if
  \begin{align*}
    \lim_{\gamma \to 1}(1-\gamma)^{-n}\ (V_{\gamma}^{\polopt}(s) - V_{\gamma}^{\pol}(s)) \geqslant 0 \tpkt
  \end{align*}
\end{definition*}

\subsection{\(\mathbf{(-1)}\)-Discount-Optimality\cite{Mahadevan96_AnAveragerewardReinforcementLearningAlgorithmForComputingBiasoptimalPolicies}.}

Here we provide insights in the algorithm and
\(n\)-discount-optimality, where we concentrate on \(n=-1\). Recall that the discounted state value
can be expanded by the Laurent series expansion:
\(V_{\gamma}^{\pol} = \frac{\avgrew^{\pol}(s)}{1-\gamma} + V^{\pol} + e_{\gamma}^{\pol}(s)\), where
\(\lim_{\gamma \to 1} e_{\gamma}^{\pol}(s) = 0\)

\begin{align*}
  \lim_{\gamma \to 1} (1-\gamma)^{1} \cdot (V_{\gamma}^{\polopt}(s) - V_{\gamma}^{\pol}(s)) \geqslant 0\\
  \lim_{\gamma \to 1} (1-\gamma) \cdot (\frac{\avgrew^{\polopt}(s) - \avgrew^{\pol}(s)}{1-\gamma} + V^{\polopt}(s) - V^{\pol}(s) + e_{\gamma}^{\polopt}(s) - e_{\gamma}^{\pol}(s)) \geqslant 0\\
  \lim_{\gamma \to 1} (\avgrew^{\polopt}(s) - \avgrew^{\pol}(s) + (1-\gamma) \cdot (V^{\polopt}(s) - V^{\pol}(s) + e_{\gamma}^{\polopt}(s) - e_{\gamma}^{\pol}(s)) \geqslant 0\\
  \avgrew^{\polopt}(s) - \avgrew^{\pol}(s) \geqslant 0\\
\end{align*}

That is a policy \(\pol\) which ought to be (\(-1\))-discount-optimal has to maximise the average reward
\(\rho^{\pol}(s)\) over all states \(s\).

\subsection{\(\mathbf{0}\)-Discount-Optimality\cite{Mahadevan96_AnAveragerewardReinforcementLearningAlgorithmForComputingBiasoptimalPolicies}.}

Note that a policy can only be \(0\)-discount-optimal if it is \(-1\)-discount-optimal, thus
\(\avgrew^{\polopt}(s)=\avgrew^{\pol}(s)\). Furthermore, recall that
\(\lim_{\gamma \to 1} e_{\gamma}^{\pol}(s) = 0\).

\begin{align*}
  \lim_{\gamma \to 1} (1-\gamma)^{0} \cdot (V_{\gamma}^{\polopt}(s) - V_{\gamma}^{\pol}(s)) \geqslant 0\\
  \lim_{\gamma \to 1} (\frac{\avgrew^{\polopt}(s) - \avgrew^{\pol}(s)}{1-\gamma} + V^{\polopt}(s) - V^{\pol}(s) + e_{\gamma}^{\polopt}(s) - e_{\gamma}^{\pol}(s)) \geqslant 0\\
  \lim_{\gamma \to 1} (\frac{0}{1-\gamma} + V^{\polopt}(s) - V^{\pol}(s)) \geqslant 0\\
  V^{\polopt}(s) - V^{\pol}(s) \geqslant 0\\
\end{align*}

Therefore a \(0\)-discount-optimal policy \(\pol\) has to maximise the bias values
\(V^{\pol}(s)\) for all states \(s\).

\vfill
\pagebreak

\subsection{\(\mathbf{n}\)-Discount-Optimality for \(\mathbf{n \geqslant 1}\).}

The following derivation provides an important insight to the analysis. Recall that for unichain
MDPs the average reward \(\avgrew^{\pol}(s)\) for all states \(s\) is equal and stated as
\(\avgrew^{\pol}\). Furthermore, as the policy is \(0\)-discount-optimal
\(V^{\polopt}(s) = V^{\pol}(s)\).

\begin{align*}
  \lim_{\gamma \to 1} (1-\gamma)^{-n} \cdot (V_{\gamma}^{\polopt}(s) - V_{\gamma}^{\pol}(s)) & \geqslant 0\\
  \lim_{\gamma \to 1} (1-\gamma)^{-n} \cdot ( \frac{\avgrew^{\polopt}(s)}{1-\gamma} + V^{\polopt}(s) + e_{\gamma}^{\polopt}(s)  %& \\
  - \frac{\avgrew^{\pol}(s)}{1-\gamma} - V^{\pol}(s) - e_{\gamma}^{\pol}(s) ) & \geqslant 0\\
  \lim_{\gamma \to 1} (1-\gamma)^{-n} \cdot ( e_{\gamma}^{\polopt}(s) - e_{\gamma}^{\pol}(s) ) & \geqslant 0\\
\end{align*}

As stated before \(e_{\gamma}^{\polopt}(s)\) approaches 0 as \(\gamma \to 1\). Therefore, it is
important to note that for \(n>0\) we analyse the case when \(\gamma\) is strictly less than \(1\). This
means that the number of actions to reach a desired goal is taken into account.
        %         The ratio of long-term to short-term is provided by the discount factor \(\gamma\).
Therefore, a \(\infty\)-discount-optimal policy \(\pol\) has to maximise the error term
$e_{\gamma}^{\pol}(s)$ for all states \(s\). That is, an \(\infty\)-discount-optimal algorithm has to
choose the action with the largest error term \(e_{\gamma}^{\pol}(s)\) once \(\gamma \to 1\).
However, as the error term depends on infinitely many sub-terms simply estimating these and summing
up does not work.

\begin{figure*}[t]
  \centering
  \begin{tikzpicture}[scale=8]
    \draw[->] (0,0) -- (1.0,0) node[right] {$\gamma$};
    \draw[->] (0,0) -- (0,0.8) node[above] {$\mathbb{R}$};
    \draw[scale=1,domain=0.001:0.85,smooth,variable=\x,blue] plot ({\x},{0.1/(1-\x)+0.2});
    \draw[scale=1,domain=0.001:0.865,smooth,variable=\x,red] plot ({\x},{0.1/(1-\x)+0.2-0.2*(1-\x)^0.5});

        %         Labels
    \draw[blue] (0.6,0.64) node () {$\frac{\avgrew^{\pol}(s)}{1-\gamma} + V^{\pol}(s)$};
    \draw[red] (0.875,0.58) node () {$V_{\gamma}^{\pol}(s)$};
    \draw (-0.015,0.3) -- (0.015,0.3);
    \draw (-0.2, 0.3) node[align=left] () {$\avgrew^{\pol}(s) + V^{\pol}(s)$};

    \draw (-0.015,0.1) -- (0.015,0.1);
    \draw (-0.111, 0.1) node[] () {$R^{\pol}(s)$};

    \draw (0.9,-0.015) -- (0.9,0.015) node[below, yshift=-0.2cm] () {$1$};
    \draw (0.75,-0.015) -- (0.75,0.015) node[below, yshift=-0.2cm] () {$\gamma_{1}$};
    \draw (0.20,-0.015) -- (0.20,0.015) node[below, yshift=-0.2cm] () {$\gamma_{0}$};

    \draw (0.5,0.4) -- (0.5,0.258578644) node[midway,left, yshift=-0.2cm] () {$e_{\gamma}^{\pol}(s)$};

    \draw (0.2,0.146114562) -- (0.75,0.146114562) node[midway, below] () {$\gamma_{1}-\gamma_{0}$};
    \draw (0.75,0.146114562) -- (0.75,0.5) node[midway,right] () {$V_{\gamma_{1}}^{\pol}(s)-V_{\gamma_{0}}^{\pol}(s)$};

  \end{tikzpicture}
  \caption{Visualisation of the monotonically increasing state values for a state $s$ and the
    corresponding decreasing error term $e_{\gamma}^{\pol}(s)$ as $\gamma$ approaches 1. }
  \label{fig:e}
\end{figure*}

Therefore, the idea is to use two discounted state-values with different $\gamma$'s to infer the
slope of the error term. Figure~\ref{fig:e} illustrates the idea. Here $\gamma_{1}$ and $\gamma_{0}$
are used to estimate the difference of \(V_{\gamma_{1}}^{\pol}(s)\) and
\(V_{\gamma_{0}}^{\pol}(s)\). As the average reward and the bias values are equal (recall
\(0\)-discount-optimality) the difference is a direct estimate of the slope of the error term. Thus
the larger the increase of the difference of the discounted state values when comparing
\(0\)-discount-optimal actions the better the action. However, for this to hold true we have to
prove strict monotonicity of
\(V_{\gamma}^{\pol}(s) = \frac{\avgrew^{\pol}(s)}{1-\gamma} + V^{\pol}(s) + e_{\gamma}^{\pol}(s)\)
under increasing $\gamma$. In the sequel we assume \(\avgrew^{\pol}(s) \geqslant 0\). Note that this
assumption is easily met by adding a constant reward for any action in cases where
\(\avgrew^{\pol}(s) < 0\). This assumption eases the following analysis and makes sense as usually
we are interested in problems which accumulate positive average reward, e.g. profit or points, over
time.

\begin{remark}
  Nonetheless, it is an important insight that if \(\avgrew^{\pol}(s) < 0\) then
  \(\frac{\avgrew^{\pol}(s)}{1-\gamma} + V^{\pol}(s)\) approaches negative infinity (as opposed to
  positive infinity, cf. Figure~\ref{fig:e}). Therefore, in such cases the following optimisation
  objectives would need to be inverted.
\end{remark}

\begin{lemma}
  \label{lem:err}
  The error term
  \(e_{\gamma}^{\pol}(s) = \sum_{m=1}^{\infty}(\frac{1-\gamma}{\gamma})^{m} \cdot y_{m}\) strictly
  monotonically decreases as $\gamma$ increases.
\end{lemma}

\begin{proof}
        %         S[t]{Is the following formula (indices) correct?}
  Note that \(e_{\gamma}^{\pol}(s) = \sum_{m=1}^{\infty}(\frac{1-\gamma}{\gamma})^{m} \cdot y_{m}\),
  where the sign of \(y_{m}\) alternates in each step. This is due to the fact that
  \(y_{m} = \E_{\pol} [ y_{m} ] - y_{m-1}\) for all \(m \geqslant 1\)~\cite[p.346]{Puterman94}, that
  is \(y_{m}\) only depends on \(y_{m-1}\) and the underlying (stationary) policy. Further \(y_{0}\)
  is the bias value \(V^{\pol}(s)\).
        %
  We consider three cases:
  \begin{enumerate}
  \item[1)]
    \begin{minipage}[t]{0.17\textwidth}
      \(\gamma = 0.5\):
    \end{minipage}
    The factor \((\frac{1-\gamma}{\gamma})^{m}\) is $1$.
  \item[2)]
    \begin{minipage}[t]{0.17\textwidth}
      \(0.5 < \gamma < 1\):
    \end{minipage}
    The factor \((\frac{1-\gamma}{\gamma})^{m}\) is $<1$ and strictly monotonically converging towards $0$.
  \item[3)]
    \begin{minipage}[t]{0.17\textwidth}
      \(0 < \gamma < 0.5\):
    \end{minipage}
    The factor \((\frac{1-\gamma}{\gamma})^{m}\) is $>1$ and strictly monotonically converging towards $\infty$.
  \end{enumerate}

  \paragraph{Case 1)}
  { As \(\frac{1-\gamma}{\gamma} = 1 \) the term reduces to
    \(e_{\gamma}^{\pol}(s) = \sum_{m=1}^{\infty} y_{m}^{\pol}\). We use the definition
        %
    \begin{align*}
      y_{m}^{\pol}=(-1)^{m} H_{\pol}^{m+1} h_{\pol} \tcom
    \end{align*}
    %
    where \(H_{\pol}\) is the deviation matrix defined as
    %
    \begin{align*}
      H_{\pol} = \clim_{N \to \infty} \sum_{t=0}^{N-1}{P^{t}-P^{\star}} \tcom
    \end{align*}
    \(\clim\) the Cesaro limit\footnote{Recall that the Cesaro limit (with degree \(1\)) is only
      required in periodic MDPs to ensure stationary matrices. For aperiodic MDPs they can be read
      as normal limits.~\cite[p.592ff]{Puterman94}}, \(P^{\star}\) the stationary matrix defined as
    \(P^{\star} = \clim_{N \to \infty}P^{N}\) and \(h_{\pol}\) a column vector holding the bias values
    of the states \cite[]{Puterman94,MillerVeinott1969}. Thus, we get
        %
    \begin{align*}
      e_{\gamma}^{\pol}(s) & = \sum_{m=1}^{\infty}y_{m}^{\pol}(s) = \sum_{m=1}^{\infty}{y_{2m}^{\pol}(s) + y_{2m+1}^{\pol}(s)}
                             = \sum_{m=1}^{\infty} H^{2m+2} h - H^{2m+1} h \\
                           & = \sum_{m=1}^{\infty} (H^{2m+2} - H^{2m+1}) h \tpkt
    \end{align*}

    % Wlog. assume all entries in \(H\) are positive. Therefore,
    It suffices\footnote{This claim has not been proven yet!} to show that $H^{2m+2} - H^{2m+1} < 0$
    for all $m \geqslant 1$ to prove strict monotonicity of $e_{\gamma}^{\pi}(s)$.
    % \MS[t]{why should that prove monotonicity? Rethink!!!}
    However, this directly follows as for MDPs with at least two states \(H-1 < 0\) in
    %
    \begin{align*}
      e_{\gamma}^{\pol}(s) = \sum_{m=1}^{\infty} (H^{2m+2} - H^{2m+1}) h = \sum_{m=1}^{\infty} H^{2m+1} (H - 1) h \tpkt
    \end{align*}
    %
  }

  \paragraph{Case 2)}{ As the factor \((\frac{1-\gamma}{\gamma})^{m}\) is $<1$ and strictly
    monotonically decreasing for an increasing $m \geqslant 1$, we use the same argument as in the
    previous case (Case 1) with which the claim follows. }

  \paragraph{Case 3)}{ This part of the proof is open!

    % Recall the Laurent Series expansion only holds when \(0 <
    % \frac{1-\gamma}{\gamma} < \norm{H_{\pi}}^{-1}\),
    % where for a finite matrix \(C = (c_{ij})\) the norm \(\norm{C}\) is defined as
    % \(\norm{C} \coloneqq \max_{i} \sum_{j} |c_{ij}|\).

    % \begin{align*}
    %   e_{\gamma}^{\pol}(s) & = \sum_{m=1}^{\infty}y_{m}^{\pol}(s) = \sum_{m=1}^{\infty}{y_{2m}^{\pol}(s) + y_{2m+1}^{\pol}(s)}\\
    %   & = \sum_{m=1}^{\infty} (\frac{1-\gamma}{\gamma})^{2m+1} H^{2m+2} h -
    %   (\frac{1-\gamma}{\gamma})^{2m}H^{2m+1} h \\
    %   & = \sum_{m=1}^{\infty} (\frac{1-\gamma}{\gamma})^{2m} H^{2m+1}((\frac{1-\gamma}{\gamma}) H - 1) h \tpkt
    % \end{align*}

          %           \MS{No! This does not prove that under two different gammas $e_{\gamma_{1}}^{\pol}(s) -
          %           e_{\gamma_{0}}^{\pol}(s)$ is decreasing}

  }

          %           We now investigate \(e^{\pol}(s) = \sum_{m=1}^{\infty}y_{m}^{\pol}(s)\) to infer properties of
          %           \(e_{\gamma}^{\pol}(s)\). Observe that we removed the factor $(\frac{1-\gamma}{\gamma})^{m}$
          %           depending on a concrete \(\gamma\). There are three cases to distinguish for this factor under
          %           increasing $m$:

          %           In all three cases the factor does neither change the monotonicity properties nor the sign of
          %           $y_{m}$ in the term
          %           \(e_{\gamma}^{\pol}(s) = \sum_{m=1}^{\infty}(\frac{1-\gamma}{\gamma})^{m} \cdot y_{m}\).
          %           Therefore, wlog. suppose $\gamma = 0.5$ and thus \(e^{\pol}(s) = e_{\gamma}^{\pol}(s)\).

          %           This factor is positive and strictly and monotonically
          %           converging towards $0$ (resp. $\infty$) as $m$ increases and as long as \(0.5 < \gamma < 1\)
          %           (resp. $0 < \gamma < 0.5)$. Note that we are usually interested in $\gamma$ values close to $1$,
          %           as $\gamma \to 1$. \MS[t]{what happens when $\gamma < 0.5$?}
          %
\end{proof}

\begin{corollary}
  \label{cor:diff}
  For any two \(0\)-discount-optimal stationary policies $\pol_{1}, \pol_{2}$ with stationary
  transition matrices \(P_{1}\) and \(P_{2}\) respectively, the differences of the slopes of the
  error terms \(e_{\gamma}^{\pol_{1}}(s)\) and \(e_{\gamma}^{\pol_{2}}(s)\) for any \(\gamma\) is
  dependent on \(H_{\pol_{1}}\) and \(H_{\pol_{2}}\) and thus \(P_{1}\) and \(P_{2}\) solely.
\end{corollary}

\begin{proof}
  Note that due to \(0\)-discount-optimality the bias values \(h_{1} = h_{2}\) are equal for both
  policies. Therefore as for any given \(H\) the error term is determined by
  \(e_{\gamma}^{\pol}(s) = \sum_{m=1}^{\infty} ((\frac{1-\gamma}{\gamma})^{2m + 1} H^{2m+2} -
  (\frac{1-\gamma}{\gamma})^{2m} H^{2m+1}) h = \sum_{m=1}^{\infty} (\frac{1-\gamma}{\gamma})^{2m}
  H^{2m+1}( \frac{1-\gamma}{\gamma} H - 1) h \) the claim follows directly.
\end{proof}

\begin{corollary}
  \label{cor:cont}
  The error term function \(e_{\gamma}^{\pol}(s)\) for \(\gamma \to 1\) and for any given policy
  \(\pol\) is continuous.
\end{corollary}

\begin{proof}
  The claim follows directly from Corollary~\ref{cor:diff} and due to the shape of the term
  \(e_{\gamma}^{\pol}(s) = \sum_{m=1}^{\infty} (\frac{1-\gamma}{\gamma})^{m} H^{m+1} h\).
\end{proof}

\begin{theorem}
  If \(\avgrew^{\pol}(s) > 0\) then
  \(V_{\gamma}^{\pol}(s) = \frac{\avgrew^{\pol}(s)}{1-\gamma} + V^{\pol}(s) + e_{\gamma}^{\pol}(s)\) is
  strictly monotonically increasing as $\gamma$ approaches \(1\).
\end{theorem}

\begin{proof}
  Due to \(\avgrew^{\pol}(s) > 0\) and \(0 < \gamma < 1\) the term
  \(\frac{\avgrew^{\pol}(s)}{1-\gamma}\) strictly monotonically approaches infinity as
  $\gamma \to 1$. Furthermore, by Lemma~\ref{lem:err} and as
  \(\lim_{\gamma \to 1} e_{\gamma}^{\pol}(s) = 0\) the theorem follows immediately.
\end{proof}

>>>>

\section{Computational Experiments}
\label{sec:Preliminary}

@@

\begin{table}[t]
  \centering
  \begin{tabular}{|l||c|c|c|c|c|c|c|c|c|c|}
    \hline
    Parameter & $\alpha$ & $\beta$ & $\delta$ & $\gamma$ & $\epsilon$ & $p_{exp}$ & $\xi$ \\
    \hline
    Value & 0.5 & 0.15 & 0.15 & 0.15 & 0.5 & 1.0 & 0.15 \\
    \hline
  \end{tabular}
  \caption{\label{tbl:params}Parameter Setup.}
\end{table}

@@

% \definecolor{lightgray}{rgb}{0.83, 0.83, 0.83}
% \begin{table}[tb]
%   \begin{center}
%     \begin{tabular}{c|ccc|c|c||c}
%       \hline
%       70-\(\Exp\)-\(\Unif\) & WIPC & FGIC & BOC & FGIC+BOC & SUM & SFTT & SL(\%) \\
%       \hline                &
%        ESSLTA{}             &      &      &     &          &     &      &        \\
%        ANN{}                &      &      &     &          &     &      &        \\
%        ESSLTB{}             &      &      &     &          &     &      &        \\
%        BILD{}               &      &      &     &          &     &      &        \\
%       \hline                &
% %
%       \hline                &
%       70-\(\Unif\)-\(\Exp\) & WIPC & FGIC & BOC & FGIC+BOC & SUM & SFTT & SL(\%) \\
%       \hline                &
%        ESSLTA{}             &      &      &     &          &     &      &        \\
%        ANN{}                &      &      &     &          &     &      &        \\
%        ESSLTB{}             &      &      &     &          &     &      &        \\
%        BILD{}               &      &      &     &          &     &      &        \\
%       \hline                &
% %
%       \hline                &
%       70-\(\Exp\)-\(\Exp\)  & WIPC & FGIC & BOC & FGIC+BOC & SUM & SFTT & SL(\%) \\
%       \hline                &
%        ANN{}                &      &      &     &          &     &      &        \\
%        ESSLTA{}             &      &      &     &          &     &      &        \\
%        ESSLTB{}             &      &      &     &          &     &      &        \\
%        BILD{}               &      &      &     &          &     &      &        \\
%     \end{tabular}
%   \end{center}
%   \caption{\label{tbl:70} Results for a bottleneck utilisation of 70\%. }
% \end{table}

\begin{table}[tb]
  \begin{center}
    \begin{tabular}{c|rrr|c|c||c|c|c|c|c}
      \hline
      80-\(\Exp\)-\(\Unif\)   & WIPC   & FGIC    & BOC      & FGIC+BOC & SUM     & SFTT  & SFTT+FGIT & SL(\%) & Cost.p.P & \(\avgrew^{\pol}\) \\
      \hline
       \rl{0.995}             & 55.218 & 137.006 & 52.090   &          & 244.315 & 1.506 & 2.597    & 0.915  & 34.902   & 32.791             \\
      \rl{1.000}              & 67.265 & 102.180 & 175.686  &          & 345.132 & 1.517 & 2.627    & 0.908  & 49.305   & 30.777             \\
      \BILOne{}               & 45.902 & 0.000   & 734.431  &          & 780.333 & 1.319 & 1.806    & 0.352  &          &                    \\
      \BILTwo{}               & 45.734 & 80.313  & 1425.221 &          & 268.569 & 1.318 & 2.158    & 0.876  &          &                    \\
      \BILThree{}             & 45.861 & 279.723 & 30.818   &          & 356.402 & 1.318 & 3.034    & 0.975  &          &                    \\
      \hline
%
%       \hline
%       80-\(\Unif\)-\(\Exp\) & WIPC   & FGIC    & BOC      & FGIC+BOC & SUM     & SFTT  & SFTP+FGI & SL(\%) & Cost.p.P & \(\avgrew^{\pol}\) \\
%       \hline                &
%        ESSLTA{}             &        &         &          &          &         &       &          &        &          &                    \\
%        ANN{}                &        &         &          &          &         &       &          &        &          &                    \\
%        ESSLTB{}             &        &         &          &          &         &       &          &        &          &                    \\
%        BILD{}               &        &         &          &          &         &       &          &        &          &                    \\
%       \hline
% %
%       \hline
%       80-\(\Exp\)-\(\Exp\)  & WIPC   & FGIC    & BOC      & FGIC+BOC & SUM     & SFTT  & SFTP+FGI & SL(\%) & Cost.p.P & \(\avgrew^{\pol}\) \\
%       \hline                &
%        ANN{}                &        &         &          &          &         &       &          &        &          &                    \\
%        ESSLTA{}             &        &         &          &          &         &       &          &        &          &                    \\
%        ESSLTB{}             &        &         &          &          &         &       &          &        &          &                    \\
%        BILD{}               &        &         &          &          &         &       &          &        &          &                    \\
    \end{tabular}
  \end{center}
  \caption{\label{tbl:80} Results for a bottleneck utilisation of 80\%. }
\end{table}

% \definecolor{lightgray}{rgb}{0.83, 0.83, 0.83}
% \begin{table}[tb]
%   \begin{center}
%     \begin{tabular}{c|ccc|c|c||c}
%       \hline
%       80-\(\Exp\)-\(\Unif\)   & WIPC      & FGIC      & BOC       & FGIC+BOC  & SUM   & SL(\%) \\
%       \hline
%        ESSLTA{}     &           &           &           &           &       &                  \\
%        ANN{}        &           &           &           &       &       &                      \\
%        ESSLTB{}     &           &           &           &       &       &                      \\
%        BILD{}       &           &           &           &       &       &                      \\
%       \hline
% %
%       \hline
%       80-\(\Unif\)-\(\Exp\)   & WIPC      & FGIC      & BOC       & FGIC+BOC  & SUM    & SL(\%) \\
%       \hline
%        ESSLTA{}     &           &           &           &           &       &      \\
%        ANN{}        &           &           &           &           &       &      \\
%        ESSLTB{}     &           &           &           &           &       &      \\
%        BILD{}       &           &           &           &           &       &      \\
%       \hline
% %
%       \hline
%       80-\(\Exp\)-\(\Exp\) & WIPC     & FGIC      & BOC       & FGIC+BOC  & SUM   & SL(\%) \\
%       \hline
%        ANN{}     &          &           &           &           &       &      \\
%        ESSLTA{}  &          &           &           &           &       &      \\
%        ESSLTB{}  &          &           &           &           &       &      \\
%        BILD{}    &          &           &           &           &       &      \\
%     \end{tabular}
%   \end{center}
%   \caption{\label{tbl:80} Results for a bottleneck utilisation of 70\%. }
% \end{table}

% Table~\ref{tbl:res} shows the results, where we evaluate the average reward and discounted
% reinforcement learning algorithm by providing either direct reward feedback, that is the reward
% accumulated in the next period, without keeping track of any orders, as \(\ActShipped\) and
% \(\ActShippedDQN\) respectively. Further both algorithms are evaluated with keeping track of the
% order pool orders, such that each action is responsible for all orders in the order pool. These are
% labelled \(\ActOrdPool\) and \(\ActOrdPoolDQN\). For comparisons reasons we provide
% \(\BILOne-\BILSix\) and immediate release (interval release).

% The results show that at the current time we are facing issues with scaling the algorithm to the
% order release problem. Likely this is due to parameterisation issues, which we are investigating
% currently. However, it can be seen that i) the technique of keeping track of the order pool orders
% leads to better policies and ii) that despite the parameterisation issues average reward
% reinforcement learning finds better solutions than its discounted counterpart. However, the least
% costs are generated by \(\BILThree\), which shows that there is room for improvement for the
% reinforcement learning policies.

% Interesting is also to see, that all reinforcement learning variants are releasing rather late,
% leading to low finished goods inventory costs (FGIC), but high backorder costs (BOC). Furthermore,
% the agents based on the order-pool orders, namely \(\ActOrdPool\) and \(\ActOrdPoolDQN\), are able
% achieve lower work-in-process costs (WIPC) and also lower tardiness, than the other the agents
% rewarded directly on the shipped orders.

% \begin{table}[t!]
%   \centering
%   \def\arraystretch{1.2}          %  1 is the default, change whatever you need
%   \setlength\tabcolsep{4pt}
%   \begin{tabular}{|l||c|c|c|c|c|c|c|c|c|}
%     % BEGIN RECEIVE ORGTBL res2
%     \hline
%     Algorithm/KPI & SUM & BOC & FGIC & WIPC & % \%SL &
%                                                        TARD & \(\sigma\)TARD & SFTT\\
%     \hline
%     % Evaluation 1 & \multicolumn{11}{c|}{} \\
%     \ActShipped    & 1777.74 & 1322.04 & 94.49 & 361.20       & 2.24 & 1.52 & 3.44\\
%     \ActOrdPool    & 1593.03 & 1318.65 &14.01 &260.36         & 2.11 & 1.42 & 2.68\\
%     \ActShippedDQN & 1940.62 & 1570.40 &6.30 &363.92          & 2.35 & 1.59 & 3.95 \\
%     \ActOrdPoolDQN & 1618.88 & 1306.20 & 40.68& 272.00        & 2.08 & 1.38 & 2.58\\
%     \BILOne        & 1736.98 & 1510.42  &  0.00  & 226.56     & 2.04 & 1.26 & 2.16 \\
%     \BILTwo        & 1081.79 & 769.86 & 86.89   & 225.03      & 1.87 & 1.18 & 2.15\\
%     \BILThree      &  \textbf{922.36} & 362.59 &  334.47  & 225.30     & 1.74 & 1.07 & 2.15\\
%     \BILFour       & 1062.68 & 155.72  & 681.03   & 225.93    & 1.63 & 0.99 & 2.15\\
%     \BILFive       & 1380.04 & 65.45  & 1088.94    & 225.64   & 1.67 & 1.02 & 2.15\\
%     \BILSix        & 1777.77 & 25.04 &  1529.77  & 222.96     & 1.61 & 0.85 & 2.13\\
%     \imre          & 2209.97 & 12.08 &1974.72 & 223.16        & 1.58 & 0.63 & 2.14 \\
%     \hline
%     % END RECEIVE ORGTBL res2
%   \end{tabular}
%         %         \egroup

%   \caption{\label{tbl:res}Evaluation results where the monetary units are in \(k\)-values.}

%         %         \end{figure}
% \end{table}

@@

% This paper introduces deep theoretical insights in reinfocement learning and provides first evidence
% that average reward reinfocement learning is better applicable to operations research problems than
% the discounted framework. The paper describes an application of an order release model based on
% reinforcement learning. The performance is tested on a multi-product, two-stage hypothetical flow
% shop and is measured by cost, delivery and lead time related measures. We show that in the current
% version the machine learning approach is not able to outperform all other tested order release
% approaches. In the future we expect to be able to yield better results by investigating the
% parameterisation and resolving current issues when scaling average reinforcement learning to complex
% scenarios.

\MS[t]{todo}

@@
